---
title: "Monte Carlo Homework 1"
author: "Ray Su"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    df_print: paged
    highlight: kate
    number_sections: no
    theme: journal
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("DiagrammeR")
library("ggplot2")
```
# Question for Thursday
A miner is trapped in a mine with 3 doors.  Door 1 leads to a tunnel which takes him to safety after 2 hours of travel.   The second door leads to a tunnel that returns him to the mine after 3 hours of travel.  The 3rd door leads to a tunnel which returns him to the mine after 5 hours.  Assuming that the miner is at all times equally likely to choose any one of the doors, what is the expected length of time until the miner reaches safety?

```{r}
grViz("
digraph boxes_and_circles {

# add node statemetns
node [shape = polygon
      fontname = Helvetica
]
#add edge statements
Start->Door1 [label= '  p=1/3'];
Start->Door2 [label= '  p=1/3'];
Start->Door3 [label= '  p=1/3'];
Door1-> Safety [label= '  2 hours'];
Door2-> Start [label= ' 3 hours'];
Door3-> Start [label= ' 5 hours'];
}      
")
```

## To caculate the conditional expectation of the number of hours for reaching safty

X = the number of the minutes to reach safety

E(X)=E(X|Door1)P(Door1) + E(X|Door2)P(Door2) + E(X|Door3)P(Door3)=6/3+[3+E(X)]/3+[5+E(X)]/3 

Answer:E(X)=10

The oringinal code could be found from [youtube](https://www.youtube.com/watch?v=SP0yJEaWT3w).
```{r,echo=TRUE,warning=FALSE}
set.seed(20170904)
time.escape<-function(escape = 0){
    # escape = 0: No, 1: Yes
    time = 0
    while (escape ==0){
      door <-ceiling(runif(n = 1,min = 0,max = 3))
      if (door ==1){
        escape = 1
        time = time +2}
      if (door ==2) time = time+3
      if (door ==3) time = time+5
    }
    return(time)
}
n=500
time.list<-replicate(n,time.escape(0))
mean(time.list)
```
Plot
```{r}
mydata<-data.frame(
  "iter"=c(1:n),
  "Escape.time"=time.list
)
ggplot(mydata,aes(x=iter,y=Escape.time))+geom_line()+geom_hline(yintercept =mean(time.list),show.legend = TRUE,colour="red")+
  annotate("text",x= 150,y =mean(time.list)+1,label= paste("Mean of escape time=",mean(time.list),sep=""), colour = "blue")+theme_bw()

ggplot(mydata,aes(x=iter,y=Escape.time)) +
  ylim(0, NA) +
  geom_point(color = 'red', stat = 'identity') +
  geom_polygon(color = 'purple', fill=NA) +
  coord_polar(start = - pi * 1/24)
```








