---
title: "Monte Carlo Homework 2"
author: "Ray Su"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: kate
    number_sections: no
    theme: paper
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

```{r package}
library("DiagrammeR")
library("ggplot2")
```

# Question for Thursday
Hospital X is planning on opening an in-hospital certified Birth Center.They are planning to have two rooms in which women will stay for their entire labor, delivery and post-partum period. If women and/or their infants need to stay in the hospital more than 24 hours, they will be transferred to the post-partum unit.

We think we need three Birth Center birthing rooms. We will be doing about 15 births a month and estimate a average stay in the center of 34 hours. 

We need to estimate the probability of 3 or more women being in the center at the same time and maybe the probability of that happening once, twice, three times a month.

It would also be good to run the same problem with 12 births a month and 20 births a month.


# Answer
X: The number of patients arriving in the center within one day
A: The number of the event (X>=3) happening in a month

+ Assume probability of events X is a Poisson distribution.
+ Here we know 15 births per month  = >   0.5 births per day
```{r lambda 15}
set.seed(201713)
iter=10000
Prob_vector<-c()
EventA<- c()
for (i in 1:iter){
  (X<-rpois(n=30,lambda = 0.5))
  A<-length(which(X>=3))
  X_large2<-length(which(X>=3))/30
  Prob_vector<-c(Prob_vector,X_large2)
  EventA<-c(EventA,A)
}
DistA<-data.frame(table(EventA))
DistA$prob<-DistA$Freq/iter
```
## Q1: the probability of 3 or more women being in the center at the same time.
If do 10,000 times simulation: P(X>=3) = `r round(mean(Prob_vector),4) ` .
Caculete by using poisson distribution: `r ppois(2, lambda=0.5, lower=FALSE)`

The probability distribution of event A
```{r}
DistA
```

#12 births a month 
```{r lambda 12}
set.seed(201713)
iter=10000
Prob_vector<-c()
EventA<-c()
for (i in 1:iter){
  (X<-rpois(n=30,lambda = 12/30))
  A<-length(which(X>=3))
  X_large2<-length(which(X>=3))/30
  Prob_vector<-c(Prob_vector,X_large2)
  EventA<-c(EventA,A)
}
DistA<-data.frame(table(EventA))
DistA$prob<-DistA$Freq/iter
```
If do 10,000 times simulation: P(X>=3) = `r round(mean(Prob_vector),4) ` .
Caculete by using poisson distribution:`r ppois(2, lambda=12/30, lower=FALSE)`
```{r}
DistA
```

#20 births a month.
```{r lambda 20}
set.seed(201720)
iter=10000
Prob_vector<-c()
EventA<-c()
for (i in 1:iter){
  (X<-rpois(n=30,lambda = 20/30))
  A<-length(which(X>=3))
  X_large2<-length(which(X>=3))/30
  Prob_vector<-c(Prob_vector,X_large2)
  EventA<-c(EventA,A)
}
DistA<-data.frame(table(EventA))
DistA$prob<-DistA$Freq/iter
```
If do 10,000 times simulation: P(X>=3) = `r round(mean(Prob_vector),4) `.
Caculete by using poisson distribution:`r ppois(2, lambda=20/30, lower=FALSE)`
```{r}
DistA
```


# Consider the time




